---
output: github_document
---

```{r, results = 'hide', warning = FALSE, error = FALSE, message = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Installation 

The package can be installed with: 
```{r, eval=FALSE}
library(devtools)

install_github("hannahbartmn/ATP.ranking")
```

# Contents

Find out about the dataset and the weight functions with:
```{r, eval=FALSE}
help(package = "ATP.ranking")
```

# Dataset

The dataset can be accessed with: 
```{r, eval=FALSE}
data("tennis_data")
```

# References

Kovalchik, S. (2019). deuce: Resources for Analysis of Professional Tennis Data. Last viewed: 31-07-2024. url: https://github.com/skoval/deuce.

Ley, C., T. Van de Wiele and H. Van Eetvelde (2019). 'Ranking soccer teams on basis of their current strength: A comparison of maximum likelihood approaches'. In: Statistical Modelling 19.1, pp. 55–73. doi: 10.1177/1471082X18817650.

Sackmann, J. (2024). ATP Tennis Rankings, Results, and Stats. Last viewed: 31-07-2024. url: https://github.com/JeffSackmann/tennis_atp.
